The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2016-01-11 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
updated dave beam models and text

The HFSS model uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at vertex. In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.  The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging from the backplane (DOES DAVE'S MODEL HAVE THE 0.5IN GAP BETWEEN THE BACKPLANE AND THE SKIRT??). All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response. The dipoles themselves is modeled as a copper pipe of diameter XX, we neglect the dielectric PVC in which the copper pipe is actually enclosed. In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.

>>>>

The HFSS model uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at vertex. In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.  The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging 0.5\,in below the backplane. All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response. The dipoles themselves is modeled as a copper pipe of diameter XX, we neglect the dielectric PVC in which the copper pipe is actually enclosed. In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.
